\documentclass[16pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}
\usepackage[inline]{asymptote}
\usepackage{asymptote}
\usepackage{amsmath,amsthm,amssymb,amsfonts, enumitem, fancyhdr, color, comment, graphicx, environ}
\usepackage{tikz}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage{multicol}
\setlength{\columnsep}{1cm}

\pagestyle{fancy}
\setlength{\headheight}{65pt}
\def\Dot[#1](#2){\psdot[dotstyle = o, fillcolor = #1](!#2 0)}

\newcommand{\xpoint}[2][white]{%
    \pscircle[fillstyle=solid,fillcolor=#1](!#2 0){3pt}}


\rhead{Honors Math 5 Assignment 3}
\begin{document}
\Large


\paragraph{1. } A rocket traveled $12000$ miles in the first four hours. Then the rocket traveled $8000$ miles in the next four hours. What was the rocket's average speed, in miles per hour, for these $8$ hours? 
\vspace{\stretch{1}}

\paragraph{2. } Kyle, Kate, and Kendall split the cost of a pizza evenly between the three of them. If Kyle paid $\$3.24$, what was the total cost of the pizza in dollars?
\vspace{\stretch{1}}

\paragraph{3. } Each row of the Misty Moon Amphitheater has 30 seats. Rows 12 through 22 are reserved for a special group. How many seats are reserved for this group?
\vspace{\stretch{2}}

\paragraph{4. } Find $3 \cdot 5 \cdot 7 + 15 \div 3.$
\vspace{\stretch{1}}

\paragraph{5. } What is the value of $(4^3 + 2^3) - (3^3 + 1^3)$??
\vspace{\stretch{1}}

\paragraph{6. } Find $7+50+201+42+33+199+18$.
\vspace{\stretch{2}}

\paragraph{7. } Steven owns a very orderly apple tree. The tree has $12$ main branches, and each main branch has exactly $3$ smaller branches. Each smaller branch has $3$ apples, and there are $5$ leaves surrounding each apple. How many leaves are on this apple tree?$
\vspace{\stretch{1}}

\paragraph{8. } Sauron has three nickels, five dimes and five quarters. How much money does he have in cents?
\vspace{\stretch{1}}

\paragraph{9. } Assuming $a=373, b=25,$ and $c=4,$ what is the value of $c(ab)?$
\vspace{\stretch{2}}

\paragraph{10. } Compute: $55\times1212-15\times1212$ .
\vspace{\stretch{1}}

\paragraph{11. } Compute: $(4\times 19)\times 25$.
\vspace{\stretch{1}}

\paragraph{12. } Maria's family must drive $136$ miles to reach the beach. $15$ miles after beginning, they stop for gas. $23$ miles after the gas station, they stop for lunch. Then, they backtrack $2$ miles to buy swimsuits. How many more miles must they drive to reach the beach?
\vspace{\stretch{2}}

\paragraph{13. } What is the product of the reciprocal of $6$ and the reciprocal of $7$?
\vspace{\stretch{1}}

\paragraph{14. } What number does not have a reciprocal?
\vspace{\stretch{1}}

\paragraph{15. } What is the result of multiplying the reciprocal of $\frac{1}{4}$ by the reciprocal of $\frac{1}{8}$?
\vspace{\stretch{2}}

\paragraph{16. } Compute $1{,}421{,}035{,}490\div 7$.
\vspace{\stretch{1}}

\paragraph{17. } How many perfect squares are there between $5$ and $50$?
\vspace{\stretch{1}}

\paragraph{18. } Compute $a^2+b^2-c^2,$ where $a=3, b=4,$ and $c=5.$

\paragraph{19. } Grace bought $11$ tickets to a baseball game at $12$ dollars per ticket. Parker bought $3$ tickets to the same game and paid the same amount per ticket as Grace. How much did the two of them spend together?
\vspace{\stretch{1}}

\paragraph{20. } Find the reciprocal of $(3+4)$.
\vspace{\stretch{1}}

\paragraph{21. } There are $27$ students in Mr. Anderson's math class, $18$ students in Mr. LeBaron's math class, $15$ students in Mr. Spry's math class, and $24$ students in Mrs. Swanson's math class. All of these students are being split into groups for a field trip to the math museum, and each group must contain the same number of students. If there are $6$ chaperones for the field trip and each chaperone can take one group of students, how many students will be in each group?

\paragraph{22. } The five-digit number $246\underline{\hspace{5pt}}8$ is divisible by 9. What is the missing digit?
\vspace{\stretch{1}}

\paragraph{23. } Each week, between $30$ and $50$ students show up for an archery class run by Betty and Wilma. Usually the students break up into groups of equal size for target practice. However, this week, Betty noticed that she could not break the students up into multiple groups of equal size. Wilma noticed that if she and Betty both joined the students in practicing, they still could not break the archers up into groups of equal size. How many students showed up to the archery class this week?
\vspace{\stretch{1}}

\paragraph{24. } What is the smallest positive number that is prime and $10$ less than a perfect square?

\paragraph{25. } The five-digit number $246\underline{\hspace{5pt}}8$ is divisible by 9. What is the missing digit?
\vspace{\stretch{1}}

\paragraph{26. } The lengths in feet of three pieces of timber are $48,$ $72,$ and $40.$ The sawmill operator needs to cut the timber into logs of equal length with no waste. How many feet long is the greatest possible length she can cut?

\vspace{\stretch{1}}

\paragraph{27. } Planets X, Y and Z take $360$, $450$ and $540$ days, respectively, to rotate around the same sun. If the three planets are lined up in a ray having the sun as its endpoint, what is the minimum positive number of days before they are all in the exact same locations again?

\paragraph{28. } When a spaceship full of scientists landed on Planet Q, they found that $\frac{17}{40}$ of the $160$ aliens had $3$ eyes. How many aliens had $3$ eyes?
\vspace{\stretch{1}}

\paragraph{29. } Chris was given $\frac{1}{3}$ of the $84$ cookies in the cookie jar. He ate $\frac{3}{4}$ of the cookies that he was given. How many cookies did Chris eat?
\vspace{\stretch{1}}

\paragraph{30. } Flor and Sunny are making an omelet for breakfast. Flor looks at her recipe, which calls for 
 of a teaspoon of salt, and adds that amount. Sunny, unaware that that Flor has already added salt, looks at his own recipe, which uses 
 of a teaspoon of salt. He adds this into the mix. How many teaspoons of salt are now in the omelet?

\end{document}
